---
title: "Step 3.1 - Reducing the BZA using the Ident DAta"
author: "Anna Ruby"
date: "February 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing Libraries

```{r ImportLibraries, warning = FALSE, echo=FALSE}
rm(list=ls())
library(readxl)
library(tidyverse)
library(doBy)
library(caret)
library(randomForest)
library(data.table)
library(kableExtra)
library(knitr)
```

## Loading Data
All data loaded here was originally ceated by Prof. Wilhelm.

```{r LoadData}
load("../anna_data/anna_df_BZA_1.Rdata") 
load("../Data/stage8_ident.Rdata")
```

## Reducing the BZA Data

```{r ReduceData}
#Merge w/ V_COILS_BZA & filter by ident.all.df
df_BZA <- df_BZA %>%
  dplyr::inner_join(ident.all.df, by = c("CoilID" = "SID")) %>%
  dplyr::select(MAT_IDENT, CHARGEN_NR, VORBRAMME, CoilID, lTileID, everything()
  )
```


```{r LongForm}
#Converting to Long Form
df_BZA_long <- df_BZA %>%
  tidyr::gather(key=length_attr, value=measurement, -c(CHARGEN_NR, VORBRAMME, MAT_IDENT, CoilID, lTileID))
```  

#### Computing Error Descriptives

```{r Desccriptives1, echo = FALSE}
#Compute Error Descriptives
df_BZA_desc <- df_BZA_long %>% 
  dplyr::group_by(length_attr) %>% 
  dplyr::summarise(
    count = n(),
    unique = length(unique(measurement)), 
    na = sum(is.na(measurement)), 
    mean = mean(measurement, na.rm=TRUE), 
    sd = sd(measurement, na.rm = TRUE),
    min = min(measurement, na.rm=TRUE), 
    max=max(measurement, na.rm=TRUE), 
    N=sum(!is.na(measurement))
  )
df_BZA_desc %>% 
  kable("html", caption = "Variable Descriptives") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "center")
```  


```{r Plot1, echo = FALSE}
p <- ggplot(data = df_BZA_long, aes(x = measurement)) + geom_histogram(bins = 20) + facet_wrap(~length_attr, scales = "free") 
p 
```

```{r}
#Back to wide
df_BZA <- df_BZA_long %>%
  tidyr::spread(key = length_attr, value = measurement)
```

## Saving Data, Validating Data, and Final Comments
### Saving Data

Data was saved before validation in order to ensure accurate comparisons.

```{r}
save(df_BZA, df_BZA_desc, file="../anna_data/anna_df_BZA2_1.Rdata")
```  

### Validating Data

```{r}
#Validating data
rm(list=ls())
load("../anna_data/anna_df_BZA2_1.Rdata")
A_df_BZA <- df_BZA
A_df_BZA_DESC <- df_BZA_desc

rm(df_BZA, df_BZA_desc)

#Load wilhelms data
load("../Data/df_BZA2.Rdata")

anti_join(A_df_BZA, df_BZA)
#Does Not Match
anti_join(A_df_BZA_DESC, df_BZA_desc)
#good
```

The df_BZA file does not match to Prof. Wilhelm's output, as expected. The df_BZA_desc file does match. 

### Final Comments
The data was expeccted to no longer match to Prof. Wilhelm's output, due to the first part of Step 3, so this is not a surprise. Both data sets will be used in future analysis.