---
title: "Step 3 - Prepping the BZA Data"
author: "Anna Ruby"
date: "February 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing Libraries

```{r ImportLibraries, echo = FALSE}
rm(list=ls())
library(readxl)
library(tidyverse)
library(doBy)
library(caret)
library(randomForest)
library(data.table)
library(kableExtra)
library(knitr)
library(summarytools)
```
```{r, echo = FALSE, include = FALSE}
st_css()
```
  
## Loading Data

All data here is either as found on nextcloud, or produced by Prof. Wilhelm.

```{r LoadData}
load("../Data/2018_09_20_stage8_additional_analysis2.RData")
rm(list = setdiff(ls(), "V_COILS_BZA"))
load("../Data/GR_Defects.BZA.Rdata")
load("../Data/stage8_ident.Rdata")
```

## Prepping BZA Data
```{r PrepData}
#Here we are selecting only relevent variables
#Then ordering data s.t. obs are in increasing order
#first by coilID, the TILEID
GR_Defects_BZA <- GR_Defects_BZA %>%
  dplyr::select(CoilID, TileID, ClassID, Count) %>%
  arrange(CoilID, TileID)

#Converting TileID to length region and width region
#This should preject the tiles on a logitudinal dimension
GR_Defects_BZA <- GR_Defects_BZA %>%
  dplyr::mutate(
    lTileID = TileID %/% 256,
    wTileID = TileID %% 256
    )

defects.width <- GR_Defects_BZA %>%
  dplyr::group_by(wTileID, ClassID) %>%
  dplyr::summarise(
    Count = sum(Count)
  )

defects.length.agg <- GR_Defects_BZA %>%
  dplyr::group_by(lTileID, ClassID) %>%
  dplyr::summarise(
    Count = sum(Count)
  )  

#Error Dist by geometry
defects.position.c4 <- GR_Defects_BZA %>%
  dplyr::filter(ClassID == 4) 
defects.position.c14 <- GR_Defects_BZA %>%
  dplyr::filter(ClassID == 14) 
defects.position.c15 <- GR_Defects_BZA %>%
  dplyr::filter(ClassID == 15) 
```

### Reviewing The Geometrical Error Distributions
#### Type 4 Errors
```{r Plot1, echo=FALSE}
#type 4
p <- ggplot(data = defects.position.c4, aes(x = lTileID, y=wTileID, col=Count)) + geom_point(alpha=0.8, size=0.8) + ggtitle("Error Distribution According to Surface Inspection (Type 4)") + labs(x="Length Segment", y="Width Segment") 
p + scale_colour_gradient(name="Count", low="grey", high="black") + scale_y_reverse()
ggsave("../images_1/step3/ErrorDistSufInspec_typ4.png")

```  

#### Type 14 Errors
```{r Plot2, echo=FALSE}
#type 14
p <- ggplot(data = defects.position.c14, aes(x = lTileID, y=wTileID, col=Count)) + geom_point(alpha=0.1, size=0.8) + ggtitle("Error Distribution According to Surface Inspection (Type 14)") + labs(x="Length Segment", y="Width Segment")
p + scale_colour_gradient(name="Count", low="red", high="red4") + scale_y_reverse()
ggsave("../images_1/step3/ErrorDistSufInspec_typ14.png")
```  

#### Type 15 Errors
```{r Plot3, echo = FALSE}
#type 15
p <- ggplot(data = defects.position.c15, aes(x = lTileID, y=wTileID, col=Count)) + geom_point(alpha=0.8, size=0.8) + ggtitle("Error Distribution According to Surface Inspection (Type 15)") + labs(x="Length Segment", y="Width Segment")
p + scale_colour_gradient(name="Count", low="lightblue", high="blue") + scale_y_reverse()   
ggsave("../images_1/step3/ErrorDistSufInspec_typ15.png")
```  

### Error Counts Over the Width of the Tiles
```{r}
defects.width_wide <- defects.width %>%
  tidyr::spread(key= ClassID, value = Count) %>%
  setNames( c("wTileID", "Class.4", "Class.14", "Class.15") ) %>%
  replace_na(list(Class.14=0, Class.15=0))
```

#### Type 4 Errors
```{r Plot4, echo=FALSE}
#type 4
p <- ggplot(data = defects.width_wide, aes(x = wTileID, y=Class.4)) + geom_line(col="grey2", alpha=0.5) + ggtitle("Error Distribution over Width (Type 4)") + labs(x="Width Sgment", y="Number of Type 4 Errors")
ggsave("../images_1/step3/DistOverWidth_type4.png", p)
p
```  

#### Type 14 Errors
```{r Plot5, echo = FALSE}
#type 14
p <- ggplot(data = defects.width_wide, aes(x = wTileID, y=Class.14)) + geom_line(col="red", alpha=0.5) + ggtitle("Error Distribution over Width (Type 14)") + labs(x="Width Segment", y="Number of Type 14 Errors")
ggsave("../images_1/step3/DistOverWidth_type14.png", p)
p
```  

#### Type 15 Errors
```{r PLot6, echo = FALSE}
#type 15
p <- ggplot(data = defects.width_wide, aes(x = wTileID, y=Class.15)) + geom_line(col="blue", alpha=0.5) + ggtitle("Error Distribution over Width (Type 15)") + labs(x="Width Segment", y="Number of Type 15 Errors")
ggsave("../images_1/step3/DistOverWidth_type15.png", p)
p
```  

* * *  

### Error Counts Over the Length of the Tiles

```{r}
defects.length_wide <- defects.length.agg %>%
  tidyr::spread(key= ClassID, value = Count) %>%
  setNames( c("lTileID", "Class.4", "Class.14", "Class.15") ) %>%
  replace_na(list(Class.14=0, Class.15=0))
```

#### Type 4 Errors
```{r Plot7, echo=FALSE}
#type 4
p <- ggplot(data = defects.length_wide, aes(x = lTileID, y=Class.4)) + geom_line(col="grey2", alpha=0.5) + ggtitle("Error Distribution of Length (Type 4)") + labs(x="Length Segment", y="Number of Type 4 Errors")
ggsave("../images_1/step3/DistOverLength_type4.png", p)
p
```  

#### Type 14 Errors
```{r Plot8, echo = FALSE}
#type 14
p <- ggplot(data = defects.length_wide, aes(x = lTileID, y=Class.14)) + geom_line(col="red", alpha=0.5) + ggtitle("Error Distribution of Length (Type 14)") + labs(x="Length Segment", y="Number of Type 14 Errors")
ggsave("../images_1/step3/DistOverLength_type14.png", p)
p
```  

#### Type 15 Errors
```{r Plot9, echo = FALSE}
#type 15
p <- ggplot(data = defects.length_wide, aes(x = lTileID, y=Class.15)) + geom_line(col="blue", alpha=0.5) + ggtitle("Error Distribution of Length (Type 15)") + labs(x="Length Segment", y="Number of Type 15 Errors")
ggsave("../images_1/step3/DistOverLength_type15.png", p)
p
```  

### Filter Out Large Error Counts
```{r Filter1}
#Filtering out large error counts, keeping counts <25
defects.position.c4 <- defects.position.c4 %>%
  dplyr::add_count(CoilID, lTileID)
defects.position.c14 <- defects.position.c14 %>%
  dplyr::add_count(CoilID, lTileID)
defects.position.c15 <- defects.position.c15 %>%
  dplyr::add_count(CoilID, lTileID)

run_BZA <- GR_Defects_BZA %>%
  dplyr::add_count(CoilID, lTileID) %>%
  dplyr::filter(n < 25)

#Filtering out Randbefall
BZA_tidy <- run_BZA %>%
  dplyr::filter(wTileID >5 & wTileID < 250)%>%
  dplyr::group_by(CoilID, lTileID, wTileID, ClassID) %>%
  dplyr::summarise(
    Count=sum(Count)
  )  

#New geometric error dist, with improved data
defects.position.c4.tidy <- BZA_tidy %>%
  dplyr::filter(ClassID == 4) 
defects.position.c14.tidy <- BZA_tidy %>%
  dplyr::filter(ClassID == 14) 
defects.position.c15.tidy <- BZA_tidy %>%
  dplyr::filter(ClassID == 15)
```

### PLotting Updated Geometric Error Distributions  
#### Type 4 Errors  
```{r Plot10, echo = FALSE}
#type 4
p <- ggplot(data = defects.position.c4.tidy, aes(x = lTileID, y=wTileID, col=Count)) + geom_point(alpha=0.8, size=0.8) + ggtitle("Error Distribution According to Surface Inspection (Type 4)") + labs(x="Length Segment", y="Width Segment") 
p + scale_colour_gradient(name="Count", low="grey", high="black") + scale_y_reverse()
ggsave("../images_1/step3/ErrorDistSufInspec_Filtered_typ4.png")
```

#### Type 14 Errors
```{r PLOT11, echo = FALSE}
#type 14
p <- ggplot(data = defects.position.c14.tidy, aes(x = lTileID, y=wTileID, col=Count)) + geom_point(alpha=0.1, size=0.8) + ggtitle("Error Distribution According to Surface Inspection (Type 14)") + labs(x="Length Segment", y="Width Segment")
p + scale_colour_gradient(name="Count", low="red", high="red4") + scale_y_reverse()
ggsave("../images_1/step3/ErrorDistSufInspec_Filtered_typ14.png")

```  

#### Type 15 Errors
```{r PLOT12, echo = FALSE}
#type 15
p <- ggplot(data = defects.position.c15.tidy, aes(x = lTileID, y=wTileID, col=Count)) + geom_point(alpha=0.8, size=0.8) + ggtitle("Error Distribution According to Surface Inspection (Type 15)") + labs(x="Length Segment", y="Width Segment")
p + scale_colour_gradient(name="Count", low="lightblue", high="blue") + scale_y_reverse()
ggsave("../images_1/step3/ErrorDistSufInspec_Filtered_typ15.png")
```  

```{r Defects}
defects.length <- BZA_tidy %>%
  dplyr::group_by(CoilID, lTileID, ClassID) %>%
  dplyr::summarise(
    Count = sum(Count)
  )
```

```{r AddErrorFreeTiles}
#Adding error free tiles between error affected tiles
#selecting for gaps larger than 15
defects.length$nextID <- dplyr::lead(defects.length$lTileID, default =2)

defects <- defects.length %>%
  dplyr::mutate(
    lTileID2 = case_when(nextID - lTileID > 15 ~ lTileID + ceiling((nextID - lTileID)/2))
  )

defects.lTileID2 <- defects %>%
  dplyr::select(CoilID, lTileID, lTileID2) %>%
  tidyr::gather(key=ltile_attr, value=measurement,
                lTileID, lTileID2, -CoilID) %>%
  dplyr::select(CoilID, measurement) %>%
  dplyr::rename(
    lTileID = measurement
  ) %>%
  dplyr::filter(lTileID >= 0 & lTileID <= 511) %>%
    unique() %>%
   drop_na()
```

```{r AddLongit}
#add on longitudinal tile before and after each error tile
tileID.df <- defects.lTileID2 %>%
  dplyr::mutate(
       prelTileID = lTileID - 1,
       postlTileID = lTileID + 1
       ) %>%
  tidyr::gather(key = ltile_attr, value=measurement,
                lTileID, prelTileID,  postlTileID, -CoilID
  ) %>%
  dplyr::select(CoilID, measurement) %>%
  dplyr::rename(
    lTileID = measurement
  ) %>%
  dplyr::filter(lTileID >= 0 & lTileID <= 511) %>%
    unique() 
```

```{r GenTileIds}
# Generating random tileIDs for error-free coils
#Find ident numbers for error-free coils, i.e. coils which are in V_COILS_BZA but not in GR_Defects_BZA. Generate random elements for lTileId for theses ident numbers."
ident.BZA.df <- V_COILS_BZA %>%
  dplyr::select(SID, SCHMELZ_NR, WB_VORBR_NR)
apply(ident.BZA.df, 2, function(x) {length(unique(x))})
#SID:956, Schmelz_NR:309, WB_VORB_NR:33
```

```{r FilteronIdent}
slab.ident.BZA_lack.df <- ident.BZA.df %>%
  dplyr::filter(!SID %in% ident.defects$CoilID)
apply(slab.ident.BZA_lack.df, 2, function(x) {length(unique(x))})
#SID:106, Schmelz_NR:74, WB_Vorbr_NR:24
```

```{r Merge1}
tile.ident.BZA_lack.df <- data.frame(SID = rep(sort(slab.ident.BZA_lack.df$SID), each=40), lTileID = rep(sample(0:511,40),106))

#Merging with previously generated IDs
tile.ident.BZA.df <- tileID.df  %>%
  dplyr::full_join(tile.ident.BZA_lack.df, by=c("CoilID" ="SID", "lTileID"))
```

```{r WideForm}
#Next, we turn the data frame defects into wide format and spread the error counts according to class id. Obtain full list of defect counts for BZA level.
data_BZA <- defects %>%
  dplyr::select(-nextID, -lTileID2)%>%
  tidyr::spread(key = ClassID, value = Count) %>%
  setNames( c("CoilID", "lTileID", "Class.4", "Class.14", "Class.15") ) 

data_BZA$Class.4[is.na(data_BZA$Class.4)] <- 0
data_BZA$Class.14[is.na(data_BZA$Class.14)] <- 0
data_BZA$Class.15[is.na(data_BZA$Class.15)] <- 0
apply(data_BZA, 2, function(x) {length(unique(x))})
#Apply info:
#COLITD:835, lTileID:506, Class.4:29, Class.14:17, Class.15:21
```

```{r Merge2}
#Merging w/ error free IDs
data_BZA <- tile.ident.BZA.df %>%
  dplyr::full_join(data_BZA, by=c("CoilID", "lTileID"))

data_BZA$Class.4[is.na(data_BZA$Class.4)] <- 0
data_BZA$Class.14[is.na(data_BZA$Class.14)] <- 0
data_BZA$Class.15[is.na(data_BZA$Class.15)] <- 0
apply(data_BZA, 2, function(x) {length(unique(x))})
#Apply Info:
#CoilID:941, lTileID:510, Class.4:29, Class.14:17, Class.15:21
```

```{r Merge3}
# merging extended GR_Defects_BZA with V_COILS_BZA
df_BZA <- data_BZA %>%
  dplyr::full_join(V_COILS_BZA, by=c("CoilID" = "SID"))

df_BZA$Class.4[is.na(df_BZA$Class.4)] <- 0
df_BZA$Class.14[is.na(df_BZA$Class.14)] <- 0
df_BZA$Class.15[is.na(df_BZA$Class.15)] <- 0
apply(df_BZA, 2, function(x) {length(unique(x))})
```

## Reducing the Data Set
```{r Drop1, warning = FALSE}
#dropping prodcution data Raselstein variables
var.wa <- df_BZA %>%
  dplyr::select(starts_with("WA_")) %>%
  names()

df_BZA <- df_BZA %>%
  dplyr::select(-var.wa)

#Deleting redundant indexes
var.index.dup <- df_BZA %>%
  dplyr::select(SCHMELZ_NR, contains("IDENT"), contains("_NR"), contains("BRAMMEN"), contains("UUID"), contains("NAME"), contains("SID")) %>%
  names()

df_BZA <- df_BZA %>%
  dplyr::select(-var.index.dup)

#Drop time stamps
var.ts <- df_BZA %>%
  dplyr::select(contains("ZEITPUNKT"), contains("ZEITSEL"), contains("DATUM"), contains("TIME"), contains("SEQ")) %>%
  names()
df_BZA <- df_BZA %>%
  dplyr::select(-var.ts)

#Remove Irrelevant Variables (Table from Dr. Eberle)
var.irv <- c("basePID", "ImportFlag", "A1", "Weight")
df_BZA <- df_BZA %>%
  dplyr::select(-var.irv)
```

```{r LongForm}
#Convert to long format and check availability and missing patters
df_BZA_long <- df_BZA %>%
  tidyr::gather(key=length_attr, value=measurement, -c(CoilID, lTileID))
```

#### Computing Descriptives
```{r Descriptives1, echo = FALSE}
df_BZA_desc <- df_BZA_long %>% 
  dplyr::group_by(length_attr) %>% 
  dplyr::summarise(
    count = n(),
    unique = length(unique(measurement)), 
    na = sum(is.na(measurement)), 
    N=sum(!is.na(measurement))
  )
df_BZA_desc %>% 
  kable("html", caption = "Variable Descriptives") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "center") %>%
  scroll_box(height = "400px")
```

Multiple constant variables can be observed in the data. These variables are dropped below.

```{r DropConst}
var.BZA.const <- df_BZA_desc%>%
  dplyr::filter(unique == 1) %>%
  dplyr::select(length_attr) %>%
  unlist() %>%
  as.character()

df_BZA_long <- df_BZA_long %>%
  dplyr::filter(!length_attr %in% var.BZA.const)
```

### Checking Variable Distributions
```{r VarDist}
var.BZA.bin <- df_BZA_desc%>%
  dplyr::filter(unique <= 3) %>%
  dplyr::select(length_attr) %>%
  unlist()

df_BZA_bin_long <- df_BZA_long %>%
  dplyr::filter(length_attr %in% var.BZA.bin)
```  

```{r Plot13, echo = FALSE}
p <- ggplot(data = df_BZA_bin_long, aes(x = measurement )) + geom_bar() + facet_wrap(~length_attr, scales = "free")
ggsave("../images_1/step3/VariableLevelCounts.png", plot = p)
p
```  

These variables don't seem to be binary due to some sort of masking. There is very little variability in TH_STM_IST and VB_KZ... .

```{r WideForm2}
#Back to wide form
df_BZA <- df_BZA_long %>%
  tidyr::spread(key = length_attr, value = measurement)
```

```{r Drop2}
#Dropping obs not tied to TH_STM_IST$28VA1
df_BZA <- df_BZA %>%
  dplyr::filter(TH_STM_IST == "28VA1")

#Sending most charvars to numeric (Excluding TH_STM_IST and WB_KZ_KANTENRWAERMUNG)
df_BZA <- df_BZA %>%
  dplyr::select(-c(TH_STM_IST, WB_KZ_KANTENERWAERMUNG)) %>%
  dplyr::mutate_if(is.character, as.numeric) %>%
  dplyr::bind_cols(df_BZA[,c("TH_STM_IST", "WB_KZ_KANTENERWAERMUNG")])

#Dropping piece related vars
df_BZA <- df_BZA %>%
  dplyr::select(-starts_with("WB_"), -starts_with("BA_"), -c(TH_STM_IST, WB_KZ_KANTENERWAERMUNG), -Width, -Thick, -Length, -HASPEL_T_1)
```

## Saving Data, Validating Data, and Final Comments  
### Saving Data

Data was saved before validation to ensure accurate comparisons.

```{r SaveData}
#Saving Final Output data
save(list=ls(pattern="defects"), file="../anna_data/anna_defects_1.Rdata")
save(df_BZA, file="../anna_data/anna_df_BZA_1.Rdata")
```  
  
### Validating Data

```{r ValidateData, echo = FALSE, include = FALSE, warning=FALSE}
#clearing out data files
rm(list=ls())

#~~VALIDATING DATA~~#

#loading my data
load("../anna_data/anna_df_BZA_1.Rdata")
load("../anna_data/anna_defects_1.Rdata")
#renaming
a_defects <- defects
a_defects.length <- defects.length
a_defects.length.agg <- defects.length.agg
a_defects.length_wide <- defects.length_wide
a_defects.lTileID2 <- defects.lTileID2
a_defects.position.c14 <- defects.position.c14
a_defects.position.c14.tidy <- defects.position.c14.tidy
a_defects.position.c15 <- defects.position.c15
a_defects.position.c15.tidy <- defects.position.c15.tidy
a_defects.position.c4 <- defects.position.c4
a_defects.position.c4.tidy <- defects.position.c4.tidy
a_defects.width <- defects.width
a_defects.width_wide <- defects.width_wide
a_df_BZA <- df_BZA
a_ident.defects <- ident.defects
#drop old
rm(defects, defects.length, defects.length.agg, defects.length_wide,
   defects.lTileID2, defects.position.c14, defects.position.c14.tidy,
   defects.position.c15, defects.position.c15.tidy, defects.position.c4,
   defects.position.c4.tidy, defects.width, defects.width_wide, df_BZA, ident.defects)

#Load Wilhelm's Data
load("../Data/df_BZA.Rdata")
load("../Data/stage8_defects.Rdata")

#~~VALIDATING DATA AGAINST WILHELM DATA~~#

#Compare Defects
dplyr::anti_join(defects, a_defects)
# 0 - They match!
rm(a_defects, defects)

#Compare Defects.length
dplyr::anti_join(defects.length, a_defects.length)
#0 - They match!
rm(a_defects.length, defects.length)

#Compare defects.length.agg
dplyr::anti_join(defects.length.agg, a_defects.length.agg)
#0 - They match!
rm(a_defects.length.agg, defects.length.agg)

#Compare defects.length_wide
dplyr::anti_join(defects.length_wide, a_defects.length_wide)
#0 - They match!
rm(a_defects.length_wide, defects.length_wide)

#Compare defects.lTileID2
dplyr::anti_join(defects.lTileID2, a_defects.lTileID2)
#0 - They match!
rm(a_defects.lTileID2 , defects.lTileID2)

#Compare defects.position.c14 
dplyr::anti_join(defects.position.c14, a_defects.position.c14)
#0 - They match!
rm(a_defects.position.c14, defects.position.c14)

#Compare defects.position.c14.tidy
dplyr::anti_join(defects.position.c14.tidy, a_defects.position.c14.tidy)
#0 - They match!
rm(a_defects.position.c14.tidy, defects.position.c14.tidy)

#Compare defects.position.c15 
dplyr::anti_join(defects.position.c15, a_defects.position.c15 )
#0 - They match!
rm(a_defects.position.c15, defects.position.c15)

#Compare defects.position.c15.tidy
dplyr::anti_join(defects.position.c15.tidy, a_defects.position.c15.tidy)
#0 - They match!
rm(a_defects.position.c15.tidy, defects.position.c15.tidy)

#Compare defects.position.c4 
dplyr::anti_join(defects.position.c4, a_defects.position.c4)
#Both 0 - They match!
rm(a_defects.position.c4, defects.position.c4)

#Compare defects.position.c4.tidy
dplyr::anti_join(defects.position.c4.tidy, a_defects.position.c4.tidy)
#0 - They match!
rm(a_defects.position.c4.tidy, defects.position.c4.tidy)

#Compare defects.width
dplyr::anti_join(defects.width, a_defects.width)
#0 - They match!
rm(a_defects.width, defects.width)

#Compare defects.width_wide
dplyr::anti_join(defects.width_wide, a_defects.width_wide)
#0 - They match!
rm(a_defects.width_wide , defects.width_wide)

#Compare df_BZA
dplyr::anti_join(a_df_BZA, df_BZA)
#Double check
#These do not match. 
#There are the same number of obvs, but they are 3848 that do not match
#Doesn't even match to what the Wilhelm code just outputs alone
rm(df_BZA, a_df_BZA)

#Compare ident.defects
dplyr::anti_join(ident.defects, a_ident.defects)
#0 - They match!
rm(a_ident.defects , ident.defects)
``` 

All files match excluding df_BZA, which are notably different. It is worth noting that, when comparing the data available on nextcloud as produced by Prof. Wilhelm with the output of the orginal code file, the data also does not match. The non-matching entries are not mutually exclusive between the three files: mine, Prof. Wilhelms, and that which is produced by the original code file.  

### Final Comments
Although I was able to successfully recreate the majority of the data produced from this file, there is a slight differene between the files produced here and those which were produced by Prof. Wilhelm. The following files will be provided with my data for analysis.