---
title: "Step 5 - The Final Merge"
author: "Anna Ruby"
date: "February 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing Libraries

```{r ImportLibraries, echo = FALSE, warning = FALSE}
rm(list = ls())
library(readxl)
library(tidyverse)
library(doBy)
library(caret)
library(randomForest)
library(data.table)
library(knitr)
library(kableExtra)
```

## Loading Data

I created all data used here, excluding the"stage8_ident.Rdata", created by Prof. Wilhelm. 

```{r LoadData}
load("../anna_data/anna_df_BZA2_1.Rdata")
load("../Data/stage8_ident.Rdata")
load("../anna_data/anna_nachVerschrottung_updated_1.Rdata")
```

## Merging Data
```{r Merge1}
#then aggregating all by lTileID
TV_WBW1.wide.agg <- setDT(df_WBW_length)[, lapply(.SD, mean), by = c("MAT_IDENT","lTileID")]

SGA.agg <- setDT(df_SGA[,c(3,5:6,8:65)])[, lapply(.SD, mean), by = c("MAT_IDENT", "lTileID")]
SGA.VorgHA <- setDT(df_SGA[,c(3,7)])
SGA.VorgHA.agg <- unique(SGA.VorgHA)

SGA.agg <- SGA.agg %>%
  dplyr::left_join(SGA.VorgHA.agg, by=c("MAT_IDENT"))

#Dropping unneeded large table
rm(df_SGA)
rm(SGA.VorgHA)
```

### Merging
```{r Merge2}
dataSGABZA <- df_BZA %>%
  dplyr::left_join(SGA.agg, by=c("MAT_IDENT", "lTileID")) %>%
  dplyr::select(MAT_IDENT, lTileID, CoilID, POSITION_X, RIEGELLAENGE, VORG_HAUPTAGGREGAT, Class.4, Class.14, Class.15, everything())

df <- dataSGABZA %>%
  dplyr::left_join(TV_WBW1.wide.agg, by=c("MAT_IDENT", "lTileID"))
```

## Saving Data, Validating Data, and Final Comments  
### Saving Data  
Data was saved before validation to ensure accurate comparisons.
```{r SaveData}
save(df, file="../anna_data/anna_merged_data_1.Rdata")
``` 

### Validating Data
```{r ValidateData}
rm(list = ls())
load("../anna_data/anna_merged_data_1.Rdata")

#Mydata
a_df <- df
rm(df)

#Wilehlm Data
load("../Data/stage8_merged_data.Rdata")

anti_join(a_df, df)
#Off by about 1700 Obvs
```

 
### Final Comments
The final merge has resulted in a few different observations than in the original data set, but, as I've reviewed the files numerous times and not found any sincerely worrying differences, I'll be using this output for all of my modeling.